Partridge: An effective system for the automatic classification of the types of academic papers

### 2013-05-20 doc/bcspaper/article.tex
First draft of introduction

%% RECOMMENDED %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[graybox]{svmult}
%
%% choose options for [] as required from the list
%% in the Reference Guide
%
\usepackage{mathptmx}       % selects Times Roman as basic font
\usepackage{helvet}         % selects Helvetica as sans-serif font
\usepackage{courier}        % selects Courier as typewriter font
\usepackage{type1cm}        % activate if the above 3 fonts are
                             % not available on your system
%
\usepackage{makeidx}         % allows index generation
\usepackage{graphicx}        % standard LaTeX graphics tool
%                             % when including figure files
\usepackage{multicol}        % used for the two-column index
\usepackage[bottom]{footmisc}% places footnotes at page bottom
%
%% see the list of further useful packages
%% in the Reference Guide
%
\makeindex             % used for the subject index
%                       % please use the style svind.ist with
%                       % your makeindex program
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
\begin{document}

\title{Partridge: An effective system for the automatic classification of the types of academic papers}
\titlerunning{Partridge: classifying academic papers}
% Use \titlerunning{Short Title} for an abbreviated version of
% your contribution title if the original one is too long
\author{James Ravenscroft and Maria Liakata and Amanda Clare}
% Use \authorrunning{Short Title} for an abbreviated version of
% your contribution title if the original one is too long
\institute{James Ravenscroft \at Department of Computer Science, Aberystwyth University, Aberystwyth, SY23 3DB, UK  \email{jrr9@aber.ac.uk}
\and Maria Liakata \at Name, Address of Institute \email{name@email.address}
\and Amanda Clare \at Department of Computer Science, Aberystwyth University, Aberystwyth, SY23 3DB, UK \email{afc@aber.ac.uk}}
%
% Use the package "url.sty" to avoid
% problems with special characters
% used in your e-mail or web address
%
\maketitle

@@

\section{Introduction}
\label{sec:1}
Introduce paper search, CoreSC and SAPIENTA \cite{Liakata2012}, Partridge as a platform, and random forests as a technology

@@

Discuss in more detail how Partridge processes papers, how types were chosen, how papers were acquired and how the machine learning is conducted (features, algorithm, libraries, validation methods).

>>>>

% RECOMMENDED %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass{svmult}
%
%% choose options for [] as required from the list
%% in the Reference Guide
%
\usepackage{mathptmx}       % selects Times Roman as basic font
\usepackage{helvet}         % selects Helvetica as sans-serif font
\usepackage{courier}        % selects Courier as typewriter font
\usepackage{type1cm}        % activate if the above 3 fonts are
                             % not available on your system
%
\usepackage{makeidx}         % allows index generation
\usepackage{graphicx}        % standard LaTeX graphics tool
%                             % when including figure files
\usepackage{multicol}        % used for the two-column index
\usepackage[bottom]{footmisc}% places footnotes at page bottom
%
%% see the list of further useful packages
%% in the Reference Guide
%
%\makeindex             % used for the subject index
%                       % please use the style svind.ist with
%                       % your makeindex program
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
\begin{document}

\title*{Partridge: An effective system for the automatic classification of the types of academic papers}
\titlerunning{Partridge: classifying academic papers}
% Use \titlerunning{Short Title} for an abbreviated version of
% your contribution title if the original one is too long
\author{James Ravenscroft \and Maria Liakata \and Amanda Clare}
% Use \authorrunning{Short Title} for an abbreviated version of
% your contribution title if the original one is too long
\institute{James Ravenscroft, Amanda Clare \at Department of Computer Science, Aberystwyth University, Aberystwyth, SY23 3DB, UK  \email{jrr9@aber.ac.uk}
\and Maria Liakata \at Name, Address of Institute \email{name@email.address}}

%
% Use the package "url.sty" to avoid
% problems with special characters
% used in your e-mail or web address
%
\maketitle

@@

\section{Introduction}
\label{sec:1}
Since the advent of the `Digital Age' and the ability of computers to copy and reproduce information for a negligible cost, the amount of information available to researchers has been increasing drastically.  B-C Bj\"{o}rk (2009) estimates that approximately 1.4 Million papers were published in the year 2006 alone\cite{bjork2009}.
As available information increases, relevant material becomes progressively more difficult to find manually and the need for an automated information retrieval tool more apparent.
There are already a large number of information retrieval and recommendation systems for scientific publications.  Many of these systems, such as AGRICOLA (\url{http://agricola.nal.usda.gov/}), the Cochrane Library(\url{http://www.thecochranelibrary.com/}) and Textpresso (\url{http://www.textpresso.org/}) index only publications from predefined journals or topics (for the above examples, Agriculture, Biology and Bioinformatics respectively).
Unfortunately, these domain specific indexing systems usually only contain a small subset of papers, excluding potentially crucial literature because it does not quite fit into the subject domain. 
%This problem is often exacerbated by the decision to leave out some papers and articles because the system administrators do not have permission from the author or publisher to include them. 
The value of these systems to their users is often restricted by the small proportion of available literature that they index, forcing researchers to use multiple, domain specific, search engines for their queries.
In contrast, there are also a number of interdisciplinary indexing systems and online journals such as arXiv( \url{http://arxiv.org/}), PloSOne(\url{http://plosone.org/}), and JSTOR (\url{http://www.jstor.org/}), that try to incorporate wide ranges of papers from as many disciplines as possible. The traits of these systems often complement those of their domain-specific counterparts; they provide a comprehensive collection of literature but insufficient filtering and indexing capabilities.
One of the most publicised and well known interdisciplinery scientific literature search systems is Google Scholar (\url{http://scholar.google.com}). Google offers advanced query options specific to Scholar that allow searching by author, year and for words that occur only in the document title.

However, the document title is just one part of the important structure to be found within a scientific document.
Liakata \emph{et al.} (2012) describe a system for automatically processing and classifying sentences in a research paper according to the core scientific concept (CoreSC) that they describe\cite{Liakata2012}. 
There are 13 CoreSCs, including {\em hypothesis}, {\it background}, {\em result}, {\em method} and {\em conclusion}.
CoreSC labels can be allocated to all sentences in a scientific paper in order to identify which scientific concept each sentence encapsulates.
SAPIENTA (\url{http://www.sapientaproject.com}) is a machine learning application which can automatically annotate all sentences in a scientific paper with their CoreSC labels. It was trained using a corpus of physical chemistry and biochemistry research papers whose sentences were manually annotated using the CoreSC\cite{LIAKATA10.644} scheme. 
An intelligent academic information retrieval system can use this information in order to provide better filtering and search capabilities for researchers. 
The ability to search for phrases and keywords by CoreSC will facilitate context-aware keyword search, that allows researchers to only accept papers where a term appears in sentences with a specific CoreSC label.
This can be used to greatly improve both the precision with which researchers are able to perform searches for scientific literature and the accuracy of those searches in terms of relevance to the reader.

The type of a paper ({\em review}, {\em case study}, {\em research}, {\em perspective}, etc) is another useful feature through which a user can narrow down the results of a search. 
The type of a paper can then be used to augment queries.
For example, a user may search for a {\em review} paper containing the keywords ``PCR microfluidics'', or a {\em research} paper with a {\em hypothesis} containing the keywords ``cerevisiae'' and ``glucose''.   
Such paper types are not yet standardised by journals.
We expect the structure of a paper to reflect its paper type. 
For example, review papers would be expected to contain a large amount of background material.
In this article, we describe the application of machine learning (using random forests) to create predictive models of a paper's type, using the distribution of CoreSC labels found in the full text of the paper.

This model of paper type is currently in use in our Partridge system, which has been created as an intelligent full-text search platform for scientific papers. 
Partridge can make use of automatically derived CoreSC sentence labels and automatically derived paper types, to allow deeper information queries.  
We discuss the reliability of this model of paper types and the insights that have been gained for the authorship of papers.

@@

Discuss in more detail how Partridge processes papers (PDFX, sentence splitting)

how types were chosen,

how papers were acquired

how the machine learning is conducted (features, algorithm, libraries, validation methods).
